On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-16 0_abstract.tex
bits...

\begin{abstract}
\sm{I don't like this abstract...}

Magnitude estimation is a psychophysical scaling technique for the
measurement of sensation, where observers assign numbers to stimuli in
response to their perceived intensity.
We investigate the use of magnitude estimation for judging the
relevance of documents for information retrieval
evaluation, carrying out a large-scale user study across 18 TREC topics
and collecting
over 50,000 magnitude estimation judgments using crowdsourcing.
Our analysis shows that, on average, magnitude estimation judgments are
rank-aligned with ordinal judgments made by expert relevance assessors.
%An advantage of magnitude estimation is that users can chose their own
%scale for judgments, allowing deeper investigations of user perceptions
%than when categorical scales are used.

>>>>

\begin{abstract}

Magnitude estimation is a psychophysical scaling technique for the
measurement of sensation, where observers assign numbers to stimuli in
response to their perceived intensity.
We investigate the use of magnitude estimation for judging the
relevance of documents for information retrieval
evaluation, carrying out a large-scale user study across 18 TREC topics
and collecting
over 50,000 magnitude estimation judgments using crowdsourcing.
%
Our analysis shows that magnitude estimation judgments 
\textcolor{red}{ can be
reliably collected using crowdsourcing,  are competitive in terms of
assessor cost, and}, on average, they are
rank-aligned with ordinal judgments made by expert relevance assessors.

%An advantage of magnitude estimation is that users can chose their own
%scale for judgments, allowing deeper investigations of user perceptions
%than when categorical scales are used.
